Collective SU($n$) spin model dynamics

### 2020-08-25 sun_phases/sun_dynamics_notes.tex
added initial state with back-to-back spins

  A vanishing norm can only occur due to fine-tuned cancellations that make the expectation value of $\sum_j x^V_{\alpha j} \Pi^V_j$ difficult to estimate due to the presence of measurement errors and shot noise.}.

>>>>

  A vanishing norm can only occur due to fine-tuned cancellations that make the expectation value of $\sum_j x^V_{\alpha j} \Pi^V_j$ difficult to estimate from noisy data on $\bk{\Pi^V_j}_\rho$.}.
